Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
small stuff: some refs and some figure improving.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
% TODO(pronobis): general comment about many .... approches to place categorization.
The problem of room categorization based on visual information was first addressed
in the computer vision community. In this case, the research focused mainly on the
problem of classifying single images captured in indoor or outdoor environments
(scene classification). At the same time, robotics researchers initially employed
the 2D laser range sensor being much more robust to variations occurring in the
environment and much easier to handle computationally in real time.

@@

Probabilistic representations have been frequently used for spatial modelling
in robots operating in the real-world\cite{gross2009toomas,maierprobabilistic}.
Boutell et al.\cite{boutell2006factor} have studied outdoor scene classification using
\emph{factor graphs} and modelling spatial relations between objects in the scene
to extract better knowledge from semantic (high-level) features.

@@

In the presented case, the conditional probability is approximated by the graphical model $G$
produced by the conceptual layer.
\autoref{fig:conditional-prob-graph} represents a possible graph $G$ built from the conceptual
layer to represent the conditional probability on the sensed variables $x$.
$P_G(x)$ is used as an approximation for $P(x|\overline{novel})$.

@@

\subsection{Unconditional Probability}
\label{sec:unconditional-prob}
One of the hardest problems is that on most cases a novelty detection system only
has access to the known data.
Under that the best approach is to define a threshold assuming that $P(x)$ is
constant through all the input space.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
% TODO(pronobis): general comment about many .... approches to place categorization.
The problem of room categorization based on visual information was first addressed
in the computer vision community. In this case, the research focused mainly on the
problem of classifying single images captured in indoor or outdoor environments
(scene classification)\cite{oliva2006building,torralba2003contextual}.
At the same time, robotics researchers initially employed
the 2D laser range sensor being much more robust to variations occurring in the
environment and much easier to handle computationally in real time\cite{mozos2005supervised}.

@@

Probabilistic representations have been frequently used for spatial modelling
in robots operating in the real-world\cite{gross2009toomas,maier2010probabilistic}.
Boutell et al.\cite{boutell2006factor} have studied outdoor scene classification using
\emph{factor graphs} and modelling spatial relations between objects in the scene
to extract better knowledge from semantic (high-level) features.

@@

In the presented case, the conditional probability is approximated by the graphical model $G$
produced by the conceptual layer.
\autoref{fig:conditional-prob-graph} presents a possible graph $G$ built from the conceptual
layer to represent the conditional probability on the sensed variables $x$.
$P_G(x)$ is used as an approximation for $P(x|\overline{novel})$.

@@

\subsection{Unconditional Probability}
\label{sec:unconditional-prob}
With only access to labelled data a common approach is to define a threshold assuming
that $P(x)$ is constant through all the samples.
